Google's Mobility reports: changes to mobility patterns during Covid-19 lock-down in Austria

### 2021-02-14 _post/2020-03-02-primary-schools-in-vienna/primary-schools-in-vienna.Rmd
main update

bgr_color<- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=background-color:).*?(?=;)")) %>% str_trim()

@@

plot_district <- df_share %>%
  filter(school_type_secondary == "matura") %>%
  group_by(district_code) %>%
  mutate(n_median = median(n_rel)) %>%
  ungroup() %>%
  mutate(district_code = fct_reorder(as_factor(district_code), n_median)) %>%
  mutate(tooltip = paste("ratio: ", scales::percent(n_rel),
    "\n",
    paste(properties_bezeichnung, properties_str,
      paste0(district_code, ". ", "district"),
      sep = ", "
    ),
    "\n",
    properties_erhalter,
    sep = ""
  )) %>%
  ggplot() +
  labs(
    title = "% of pupils leaving for secondary schools with school leaving certificate (Matura) per district",
    subtitle = "Data for 2018/2019.",
    y = "% of pupils per school leaving for schools with school leaving certificate (Matura)",
    x = "district",
    caption = my_caption
  ) +
  geom_boxplot(aes(
    x = district_code,
    y = n_rel
  ),
  fill = "transparent",
  color = "grey80",
  outlier.shape = NA
  ) +
  geom_jitter_interactive(aes(
    x = district_code,
    y = n_rel,
    color = properties_erhalter,
    tooltip = tooltip
  ),
  width = .20
  ) +
  coord_flip() +
  theme_ipsum_rc() +
  scale_color_paletteer_d("ggsci::default_jama",
    labels = c("öffentlich" = "public", "privat" = "private")
  ) +
  scale_y_continuous(
    labels = scales::label_percent(),
    limits = c(0, 1)
  ) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dotted"),
    panel.grid.minor.x = element_line(linetype = "dotted"),
    legend.position = "top",
    legend.justification = "left",
    legend.title = element_blank(),
    plot.margin = margin(l = 0, t = 0.5, b = 0.5, unit = "cm"),
    plot.background = element_rect(fill = bgr_color, color = "transparent"),
    plot.title = element_text(size = 14, face = "bold", margin = margin(b = 0, unit = "cm")),
    plot.title.position = "plot",
    plot.subtitle = element_text(size = 12, color = "grey30"),
    plot.caption.position = "plot",
    plot.caption = element_markdown(color = "grey30", hjust = c(0, 1))
  )

@@

# produce plot
plot_langauge <- df_share %>%
  mutate(tooltip = paste("ratio: ", scales::percent(n_rel),
    "\n",
    paste(properties_bezeichnung, properties_str,
      paste0(district_code, ". ", "district"),
      sep = ", "
    ),
    "\n",
    properties_erhalter,
    sep = ""
  )) %>%
  filter(school_type_secondary == "matura") %>%
  filter(properties_erhalter == "öffentl.") %>%
  ggplot() +
  labs(
    y = "AHS ratio",
    title = "Relation between AHS ratio and primary school pupils' vernacular",
    subtitle = str_wrap(
      "Note that AHS ratio are school level data; 
info on vernacular is district level data. 
Only public schools. Hover over dots to get details.",
      150
    ),
    caption = my_caption,
    x = "% of primary school pupils with non-German vernacular per district"
  ) +
  geom_jitter_interactive(aes(
    x = non_german_perc,
    y = n_rel,
    tooltip = tooltip
  )) +
  geom_smooth(aes(
    x = non_german_perc,
    y = n_rel
  ),
  method = "lm", formula = y ~ x
  ) +
  scale_y_continuous(
    labels = scales::percent,
    minor_breaks = NULL
  ) +
  scale_x_continuous(
    labels = scales::label_percent(scale = 1),
    minor_breaks = NULL,
    limits = c(0, 100)
  ) +
  scale_color_paletteer_d("ggsci::default_jama") +
  # facet_wrap(vars(properties_erhalter))+
  hrbrthemes::theme_ipsum_rc() +
  theme(
    panel.grid.major.y = element_line(linetype = "dotted"),
    panel.grid.major.x = element_line(linetype = "dotted"),
    legend.position = "top",
    legend.justification = "left",
    legend.title = element_blank(),
    plot.margin = margin(l = 0, t = 0.5, b = 0.5, unit = "cm"),
    plot.background = element_rect(fill = bgr_color, color = "transparent"),
    plot.title = element_text(size = 14, face = "bold", margin = margin(b = 0, unit = "cm")),
    plot.title.position = "plot",
    plot.subtitle = element_text(size = 12, color = "grey30"),
    plot.caption.position = "plot",
    plot.caption = element_markdown(color = "grey30", hjust = c(0, 1))
  )

@@

plot_distance_diff <-
  plot_ly(
    data = shared_df_main,
    mode = "markers",
    type = "scatter",
    hoverinfo = "text",
    text = ~ paste(
      "abs diff AHS ratio (% points):", round((diff_abs * 100), 2),
      "</br>AHS factor:", round(diff_factor, 2),
      "</br>distance (m):", round(distance, 0),
      "</br>", tooltip
    )
  ) %>%
  add_trace(
    # text=~tooltip,
    marker = list(color = "orange"),
    x = ~distance,
    # y=~diff_factor,
    y = ~ scales::percent(diff_abs),
    showlegend = F
  ) %>%
  layout(
    title = list(
      text = "<b>Schools' different AHS ratios and geographical distance</b>",
      x = 0
    ),
    font = list(family = "Roboto Condensed"),
    xaxis = list(title = "distance between schools in meters"),
    yaxis = list(title = "absolute difference of AHS ratios (% points)"),
    plot_bgcolor = bgr_color,
    paper_bgcolor = bgr_color
  )

@@

cross_map2 <- plotly::plot_mapbox(
  data = shared_df_main,
  hoverinfo = "text",
  text = ~ paste(
    "abs diff AHS ratio (% points):", round((diff_abs * 100), 2),
    "</br>AHS factor:", round(diff_factor, 2),
    "</br>distance (m):", round(distance, 0),
    "</br>", tooltip
  )
) %>%
  plotly::add_markers(
    y = ~school_1_lat,
    x = ~school_1_long,
    color = "#FF0000" #,
    # text = ~address1
  ) %>%
  plotly::add_markers(
    y = ~school_2_lat,
    x = ~school_2_long,
    color = "#FF0000" # ,
    # text = ~address2
  ) %>%
  layout(
    mapbox = list(
      style = "mapbox://styles/zoowalk/ckjrkv7065tf519oax4nadm2k",
      margin=list(l=0,r=0,t=0,b=0,p=0),
      zoom = 10,
      center = list(
        lat = 48.21,
        lon = 16.3720798
      )
    ),
    showlegend = FALSE,
    paper_bgcolor = bgr_color
  ) %>% 
    config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))

>>>>

plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=blog-bg-color:).*?(?=;)")) %>%
  str_trim() %>% 
  str_extract(., regex("^#\\S+"))

@@

plot_district <- df_share %>%
  filter(school_type_secondary == "matura") %>%
  group_by(district_code) %>%
  mutate(n_median = median(n_rel)) %>%
  ungroup() %>%
  mutate(district_code = fct_reorder(as_factor(district_code), n_median)) %>%
  mutate(tooltip = paste("ratio: ", scales::percent(n_rel),
    "\n",
    paste(properties_bezeichnung, properties_str,
      paste0(district_code, ". ", "district"),
      sep = ", "
    ),
    "\n",
    properties_erhalter,
    sep = ""
  )) %>%
  ggplot() +
  labs(
    title = "% of pupils leaving for secondary schools with school leaving certificate (Matura) per district",
    subtitle = "Data for 2018/2019.",
    y = "% of pupils per school leaving for schools with school leaving certificate (Matura)",
    x = "district",
    caption = my_caption
  ) +
  geom_boxplot(aes(
    x = district_code,
    y = n_rel
  ),
  fill = "transparent",
  color = "grey80",
  outlier.shape = NA
  ) +
  geom_jitter_interactive(aes(
    x = district_code,
    y = n_rel,
    color = properties_erhalter,
    tooltip = tooltip
  ),
  width = .20
  ) +
  coord_flip() +
  theme_ipsum_rc() +
  scale_color_paletteer_d("ggsci::default_jama",
    labels = c("öffentlich" = "public", "privat" = "private")
  ) +
  scale_y_continuous(
    labels = scales::label_percent(),
    limits = c(0, 1)
  ) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(linetype = "dotted"),
    panel.grid.minor.x = element_line(linetype = "dotted"),
    legend.position = "top",
    legend.justification = "left",
    legend.title = element_blank(),
    plot.margin = margin(l = 0, t = 0.5, b = 0.5, unit = "cm"),
    plot.background = element_rect(fill = plot_bg_color, color = "transparent"),
    plot.title = element_text(size = 14, face = "bold", margin = margin(b = 0, unit = "cm")),
    plot.title.position = "plot",
    plot.subtitle = element_text(size = 12, color = "grey30"),
    plot.caption.position = "plot",
    plot.caption = element_markdown(color = "grey30", hjust = c(0, 1))
  )

@@

# produce plot
plot_langauge <- df_share %>%
  mutate(tooltip = paste("ratio: ", scales::percent(n_rel),
    "\n",
    paste(properties_bezeichnung, properties_str,
      paste0(district_code, ". ", "district"),
      sep = ", "
    ),
    "\n",
    properties_erhalter,
    sep = ""
  )) %>%
  filter(school_type_secondary == "matura") %>%
  filter(properties_erhalter == "öffentl.") %>%
  ggplot() +
  labs(
    y = "AHS ratio",
    title = "Relation between AHS ratio and primary school pupils' vernacular",
    subtitle = str_wrap(
      "Note that AHS ratio are school level data; 
info on vernacular is district level data. 
Only public schools. Hover over dots to get details.",
      150
    ),
    caption = my_caption,
    x = "% of primary school pupils with non-German vernacular per district"
  ) +
  geom_jitter_interactive(aes(
    x = non_german_perc,
    y = n_rel,
    tooltip = tooltip
  )) +
  geom_smooth(aes(
    x = non_german_perc,
    y = n_rel
  ),
  method = "lm", formula = y ~ x
  ) +
  scale_y_continuous(
    labels = scales::percent,
    minor_breaks = NULL
  ) +
  scale_x_continuous(
    labels = scales::label_percent(scale = 1),
    minor_breaks = NULL,
    limits = c(0, 100)
  ) +
  scale_color_paletteer_d("ggsci::default_jama") +
  # facet_wrap(vars(properties_erhalter))+
  hrbrthemes::theme_ipsum_rc() +
  theme(
    panel.grid.major.y = element_line(linetype = "dotted"),
    panel.grid.major.x = element_line(linetype = "dotted"),
    legend.position = "top",
    legend.justification = "left",
    legend.title = element_blank(),
    plot.margin = margin(l = 0, t = 0.5, b = 0.5, unit = "cm"),
    plot.background = element_rect(fill = plot_bg_color, color = "transparent"),
    plot.title = element_text(size = 14, face = "bold", margin = margin(b = 0, unit = "cm")),
    plot.title.position = "plot",
    plot.subtitle = element_text(size = 12, color = "grey30"),
    plot.caption.position = "plot",
    plot.caption = element_markdown(color = "grey30", hjust = c(0, 1))
  )

@@

plot_distance_diff <-
  plot_ly(
    data = shared_df_main,
    mode = "markers",
    type = "scatter",
    hoverinfo = "text",
    text = ~ paste(
      "abs diff AHS ratio (% points):", round((diff_abs * 100), 2),
      "</br>AHS factor:", round(diff_factor, 2),
      "</br>distance (m):", round(distance, 0),
      "</br>", tooltip
    )
  ) %>%
  add_trace(
    # text=~tooltip,
    marker = list(color = "orange"),
    x = ~distance,
    # y=~diff_factor,
    y = ~ scales::percent(diff_abs),
    showlegend = F
  ) %>%
  layout(
    title = list(
      text = "<b>Schools' different AHS ratios and geographical distance</b>",
      x = 0
    ),
    font = list(family = "Roboto Condensed"),
    xaxis = list(title = "distance between schools in meters"),
    yaxis = list(title = "absolute difference of AHS ratios (% points)"),
    plot_bgcolor = plot_bg_color,
    paper_bgcolor = plot_bg_color
  )

@@

cross_map2 <- plotly::plot_mapbox(
  data = shared_df_main,
  hoverinfo = "text",
  text = ~ paste(
    "abs diff AHS ratio (% points):", round((diff_abs * 100), 2),
    "</br>AHS factor:", round(diff_factor, 2),
    "</br>distance (m):", round(distance, 0),
    "</br>", tooltip
  )
) %>%
  plotly::add_markers(
    y = ~school_1_lat,
    x = ~school_1_long,
    color = "#FF0000" #,
    # text = ~address1
  ) %>%
  plotly::add_markers(
    y = ~school_2_lat,
    x = ~school_2_long,
    color = "#FF0000" # ,
    # text = ~address2
  ) %>%
  layout(
    mapbox = list(
      style = "mapbox://styles/zoowalk/ckjrkv7065tf519oax4nadm2k",
      margin=list(l=0,r=0,t=0,b=0,p=0),
      zoom = 10,
      center = list(
        lat = 48.21,
        lon = 16.3720798
      )
    ),
    showlegend = FALSE,
    paper_bgcolor = plot_bg_color
  ) %>% 
    config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))

### 2021-02-14 _post/2020-04-28-google-s-mobility-reportsmd/google-s-mobility-reportsmd.Rmd
main update

plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=background-color:).*?(?=;)")) %>% str_trim()

>>>>

plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=blog-bg-color:).*?(?=;)")) %>%
  str_trim() %>% 
  str_extract(., regex("^#\\S+"))
